---
title: "PreregistrationEvaluatin_Pilot_RandomSelecter"
author: "Marton Kovacs"
date: 'r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r}
library(tidyverse)
library(readxl)
library(stringi)
```

# Import data

```{r}
email_database <- read_xlsx("Data/PreregistrationEvaluation_ContancDatabase.xlsx", sheet = 1)
```

# Variable transformation

```{r}
email_database <-
  email_database %>% 
  mutate(number_of_names = stri_count_fixed(corresponding_author, " "),
         first_name = stri_extract_first(corresponding_author, regex="\\w+"),
         last_name = stri_extract_last(corresponding_author, regex="\\w+"),
         contains_osf_aspredicted = case_when(str_detect(prereg_link1, pattern = "osf") ~ 1L,
                                              str_detect(prereg_link1, pattern = "aspredicted") ~ 1L,     
                                                         TRUE ~ 0L),
         email = tolower(email))
```

# Filtering

```{r}
email_database <-
  email_database %>%
  filter(contains_osf_aspredicted == 1L)
```

```{r}
email_database <-
  email_database %>%
  distinct(corresponding_author, .keep_all = T)
```

```{r}
email_database <-
  email_database %>%
  filter(!is.na(email))
```

# EDA

Number of distinct corresponding authors:

```{r}
email_database %>% 
  distinct(corresponding_author) %>% 
  count()
```

# 1 batch
# Select 100 email addresses randomly

```{r}
email_selection <- 
  email_database %>% 
  sample_n(., 100)
```

# Select only the variables needed

```{r}
email_selection <- 
  email_selection %>% 
  select(last_name, email)
```

# Write selected database

```{r}
write_excel_csv(email_selection, "Data/PreregistrationEvaluation_Pilot_SelectedContacts.csv")
```

# 2 batch
# Read previous batches

```{r}
batch_1 <- read_csv2("Data/PreregistrationEvaluation_Pilot_SelectedContacts.csv")
```

# Exclude previous batch from the full contact base

```{r}
email_database_excluded <- 
  email_database %>% 
  anti_join(., batch_1, by = c("last_name", "email"))
```

# Select 100 email addresses randomly

```{r}
email_selection <- 
  email_database_excluded %>% 
  sample_n(., 100)
```

# Select only the variables needed

```{r}
email_selection <- 
  email_selection %>% 
  select(last_name, email)
```

# Write selected database

```{r}
write_excel_csv(email_selection, "Data/PreregistrationEvaluation_Pilot_SelectedContacts_Batch2.csv")
```

# Read previous batches

```{r}
batch_2 <- read_csv("Data/PreregistrationEvaluation_Pilot_SelectedContacts_Batch2.csv")
```

# Checking duplicates in the batches

```{r}
duplicates <- 
  batch_1 %>% 
  inner_join(., batch_2, by = c("email", "last_name"))
```

# Write duplicates

```{r}
write_csv(duplicates, "Data/PreregistrationEvaluation_Pilot_SelectedContacts_Duplicates.csv")
```