---
title: "PreregistrationEvaluation_Main_Raw_Processed"
author: "Marton Kovacs & Bence Bakos"
date: "18/12/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Load packages

```{r packages, message=FALSE, warning=FALSE}
library(tidyverse)
```

# Import data

```{r import data, message=FALSE}
raw_data <- read_tsv("Data/Main/Raw/PreregistrationEvaluation_Main_Raw.tsv")

# Clean variable names
raw_data <- janitor::clean_names(raw_data)
```

# Changing response

R_Z3mrRm2XJpVRZcd  meant to respond strongly agree: 'For the question about whether preregistration made it easier to avoid questionable research practices, I meant to select "Strongly agree", but selected "strongly disagree" by mistake. Please change my response to "Strongly Agree"'

The respondent actually gave the "Very Strongly Disagree" answer.

```{r changing response}
raw_data <- raw_data %>%
  mutate(other_qrp = case_when(response_id == "R_Z3mrRm2XJpVRZcd" ~ "Strongly Agree",
                               TRUE ~ other_qrp))
```


# Filtering responses

  * The analysis will concentrate only on the answers of the Preregistration Group and the Control Group.
  * Unfinished responses are excluded.
  * Participants who did not accept the informed consent form are excluded.
  * An attention check was used and participants who failed to pass it will be excluded.

```{r}
# Removing Qualtrics labels
label <-
  raw_data %>% 
  slice(1:2)

raw_data <-
  raw_data %>% 
  slice(-(1:2))

# Get the groups of interest
group_interest <- c("prereg", "control")

# Filtering data
filtered_data <- raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes",
         group %in% group_interest,
         group == "control" & control_attention == "4\nFour" | group == "prereg" & prereg_attention == "4\nFour")

# How many respondents do we have from the Prereg and the Control groups?
filtered_data %>% 
  count(group)

nrow(raw_data)

raw_data %>% 
  count(group)

# How many respondents were excluded because of not finished?
raw_data %>% 
  filter(finished == "True",
         progress == "100") %>% 
  nrow()

# Not agreeing to the consent form
raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes") %>% 
  nrow()

# How many respondents do we have from all the groups?
raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes",
         group == "control" & control_attention == "4\nFour" | group == "prereg" & prereg_attention == "4\nFour" | group == "other" & other_attention == "4\nFour") %>% 
  nrow()

raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes",
         group == "control" & control_attention == "4\nFour" | group == "prereg" & prereg_attention == "4\nFour" | group == "other" & other_attention == "4\nFour") %>% 
  filter(group %in% group_interest) %>% 
  nrow()

# How many respondents do we have from each research type?
filtered_data %>% 
  count(research_type)

filtered_data %>% 
  count(group)
```

# Removing irrelevant variables

```{r removing}
filtered_data <- filtered_data %>% 
  select(response_id, duration_in_seconds, control_hypothesis:prereg_qrp, planning:changed_comment, -control_attention, -prereg_attention)

glimpse(filtered_data)
```

# Tidying and recoding data

Several response variables need to be recoded to numeric values. As a first step, several keys are created to make the recoding process easier. Second, the keys are applied.

```{r tidying}
tidy_data <- 
  filtered_data %>% 
  # Gather all the columns with "prereg_" or "control_" prefix
  pivot_longer(
    cols = union(contains("prereg_"),contains("control_")),
    names_to = "variable_names",
    values_to = "values"
  ) %>% 
  # Response was forced so all NA values mean that the participant was not member of that group
  # So we can drop them
  drop_na(values) %>% 
  # Delete prefix and convert character variables to numeric
  mutate(variable_names = str_remove(variable_names, "prereg_|control_"),
         # Because there is a mismatch in the variable names between the control and prereg group
         variable_names = case_when(variable_names == "rmd" ~ "rdm",
                                    TRUE ~ variable_names)
         # values = case_when(values == "I do not know" ~ "0",
         #                    values == "Not applicable" ~ "99",
         #                    values == "Very Strongly Disagree" ~ "1",
         #                    values == "Strongly Disagree" ~ "2",
         #                    values == "Disagree" ~ "3",
         #                    values == "Neither Agree or Disagree" ~ "4",
         #                    values == "Agree" ~ "5",
         #                    values == "Strongly Agree" ~ "6",
         #                    values == "Very Strongly Agree" ~ "7",
         #                    TRUE ~ values),
         # values = as.integer(str_extract(values, "[0-9]{1,2}"))
         ) %>% 
  # Spread gathered columns to make the datatable tidy
  pivot_wider(
    names_from = variable_names,
    values_from = values
  )
```

# Grouping research fields

We group our respondents into research fields based on their responses to an open-ended question regarding their research field. We do the same for respondents who answered "Other" to our research type question.

Not preregistered: We realized that a lot of respondents provided their detailed opinion on preregistration as a comment. We will read through these comments and we will extract possible challenges mentioned in them to discuss them in the paper.

```{r fields, eval=FALSE}
fields <- tidy_data %>% 
  select(response_id, field) %>% 
  add_column(final_field = NA)

writexl::write_xlsx(fields, "Data/Main/Processed/Export/PreregistrationEvaluation_Fields_Old.xlsx")

type_other <- tidy_data %>% 
  filter(research_type == "Other") %>% 
  select(response_id, research_type_6_text) %>% 
  drop_na(research_type_6_text) %>% 
  add_column(final_research_type = NA)

writexl::write_xlsx(type_other, "Data/Main/Processed/Export/PreregistrationEvaluation_Type_Other.xlsx")

challanges <- tidy_data %>% 
  select(response_id, comment) %>% 
  drop_na(comment) %>% 
  add_column(group = NA)

writexl::write_xlsx(challanges, "Data/Main/Processed/Export/PreregistrationEvaluation_Challanges.xlsx")
```

# Write data

```{r export}
write_tsv(tidy_data, "Data/Main/Processed/PreregistrationEvaluation_Main_Processed.tsv")
```