---
title: "PreregistrationEvaluation_Main_Raw_Processed"
author: "Marton Kovacs & Bence Bakos"
date: "18/12/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Load packages

```{r packages, message=FALSE, warning=FALSE}
library(tidyverse)
```

# Import data

```{r import data, message=FALSE}
raw_data <- read_tsv(here::here("./data/main/raw/PreregistrationEvaluation_Main_Raw.tsv"))

# Clean variable names
raw_data <- janitor::clean_names(raw_data)
```

# Changing response

R_Z3mrRm2XJpVRZcd  meant to respond strongly agree: 'For the question about whether preregistration made it easier to avoid questionable research practices, I meant to select "Strongly agree", but selected "strongly disagree" by mistake. Please change my response to "Strongly Agree"'

The respondent actually gave the "Very Strongly Disagree" answer.

```{r changing response}
raw_data <- raw_data %>%
  mutate(other_qrp = case_when(response_id == "R_Z3mrRm2XJpVRZcd" ~ "Strongly Agree",
                               TRUE ~ other_qrp))
```


# Filtering responses

  * The analysis will concentrate only on the answers of the Preregistration Group and the Control Group.
  * Unfinished responses are excluded.
  * Participants who did not accept the informed consent form are excluded.
  * An attention check was used and participants who failed to pass it will be excluded.

```{r}
# Removing Qualtrics labels
label <-
  raw_data %>% 
  slice(1:2)

raw_data <-
  raw_data %>% 
  slice(-(1:2))

# Get the groups of interest
group_interest <- c("prereg", "control")

# Filtering data
filtered_data <- raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes",
         group %in% group_interest,
         group == "control" & control_attention == "4\nFour" | group == "prereg" & prereg_attention == "4\nFour")

# How many respondents do we have from the Prereg and the Control groups?
filtered_data %>% 
  count(group)

nrow(raw_data)

raw_data %>% 
  count(group)

# How many respondents were excluded because of not finished?
raw_data %>% 
  filter(finished == "True",
         progress == "100") %>% 
  nrow()

# Not agreeing to the consent form
raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes") %>% 
  nrow()

# How many respondents do we have from all the groups?
raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes",
         group == "control" & control_attention == "4\nFour" | group == "prereg" & prereg_attention == "4\nFour" | group == "other" & other_attention == "4\nFour") %>% 
  nrow()

raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes",
         group == "control" & control_attention == "4\nFour" | group == "prereg" & prereg_attention == "4\nFour" | group == "other" & other_attention == "4\nFour") %>% 
  filter(group %in% group_interest) %>% 
  nrow()

# How many respondents do we have from each research type?
filtered_data %>% 
  count(research_type)

filtered_data %>% 
  count(group)
```

# Removing irrelevant variables

```{r removing}
filtered_data <- filtered_data %>% 
  select(response_id, duration_in_seconds, control_hypothesis:prereg_qrp, planning:changed_comment, -control_attention, -prereg_attention)

glimpse(filtered_data)
```

# Tidying and recoding data

Several response variables need to be recoded to numeric values. As a first step, several keys are created to make the recoding process easier. Second, the keys are applied.

```{r tidying}
tidy_data <- 
  filtered_data %>% 
  # Gather all the columns with "prereg_" or "control_" prefix
  pivot_longer(
    cols = union(contains("prereg_"),contains("control_")),
    names_to = "variable_names",
    values_to = "values"
  ) %>% 
  # Response was forced so all NA values mean that the participant was not member of that group
  # So we can drop them
  drop_na(values) %>% 
  # Delete prefix and convert character variables to numeric
  mutate(variable_names = str_remove(variable_names, "prereg_|control_"),
         # Because there is a mismatch in the variable names between the control and prereg group
         variable_names = case_when(variable_names == "rmd" ~ "rdm",
                                    TRUE ~ variable_names)
         # values = case_when(values == "I do not know" ~ "0",
         #                    values == "Not applicable" ~ "99",
         #                    values == "Very Strongly Disagree" ~ "1",
         #                    values == "Strongly Disagree" ~ "2",
         #                    values == "Disagree" ~ "3",
         #                    values == "Neither Agree or Disagree" ~ "4",
         #                    values == "Agree" ~ "5",
         #                    values == "Strongly Agree" ~ "6",
         #                    values == "Very Strongly Agree" ~ "7",
         #                    TRUE ~ values),
         # values = as.integer(str_extract(values, "[0-9]{1,2}"))
         ) %>% 
  # Spread gathered columns to make the datatable tidy
  pivot_wider(
    names_from = variable_names,
    values_from = values
  )
```

# Grouping research fields

We group our respondents into research fields based on their responses to an open-ended question regarding their research field. We do the same for respondents who answered "Other" to our research type question.

Not preregistered: We realized that a lot of respondents provided their detailed opinion on preregistration as a comment. We will read through these comments and we will extract possible challenges mentioned in them to discuss them in the paper.

```{r fields, eval=FALSE}
# Free text research fields responses
fields <- tidy_data %>% 
  select(response_id, field) %>% 
  add_column(final_field = NA)

writexl::write_xlsx(fields, here::here("data/main/processed/PreregistrationEvaluation_Fields_Old.xlsx"))

# Free text research type responses
type_other <- tidy_data %>% 
  filter(research_type == "Other") %>% 
  select(response_id, research_type_6_text) %>% 
  drop_na(research_type_6_text) %>% 
  add_column(final_research_type = NA)

writexl::write_xlsx(type_other, here::here("data/main/processed/PreregistrationEvaluation_Type_Other.xlsx"))

# Free text comments
challenges <- tidy_data %>% 
  select(response_id, comment) %>% 
  drop_na(comment) %>% 
  add_column(group = NA)

writexl::write_xlsx(challenges, here::here("data/main/processed/PreregistrationEvaluation_Challenges.xlsx"))
```

# Write data

```{r export}
write_tsv(tidy_data, here::here("data/main/processed/PreregistrationEvaluation_Main_Processed.tsv"))
```


# Detailed Insights in the Groups

```{r detailed_insights}
# Filtering data
filtered_data <- raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes",
         control_attention == "4\nFour" | prereg_attention == "4\nFour" | other_attention == "4\nFour"
         )

# group_sorting 1 = Preregistered study that is not published
# group_sorting 2 = Preregistered study that is published
# group_sorting 3 = Published study that is neither preregistered nor a Registered Report
# group_sorting 4 = Registered Report that is not published
# group_sorting 5 = Registered Report that is published
group_details <- filtered_data %>% 
  select(group, group_sorting_1, group_sorting_2, group_sorting_3, group_sorting_4, group_sorting_5)
group_details[group_details == "No"]  <- "0"
group_details[group_details == "Yes"] <- "1"
group_details[, -1] <- apply(group_details[, -1], 2, as.numeric)

group_details_ctrl   <- as.data.frame(group_details[group_details$group == 'control', ])
group_details_prereg <- as.data.frame(group_details[group_details$group == 'prereg', ])
group_details_other  <- as.data.frame(group_details[group_details$group == 'other', ])

#nrow(group_details_ctrl); colSums(group_details_ctrl[,-1]); colMeans(group_details_ctrl[,-1])
#nrow(group_details_prereg); colSums(group_details_prereg[,-1]); colMeans(group_details_prereg[,-1])
#nrow(group_details_other); colSums(group_details_other[,-1]); colMeans(group_details_other[,-1])
```

No researchers in the control group preregistered a study that was not published or had experience with writing a Registered Report. From the `r nrow(group_details_prereg)` researchers in the preregistration group, all researchers published a preregistered and non-preregistered study. Furthermore, `r sum(group_details_prereg$group_sorting_1)` indicated that they had preregistered a study that was not published. Here it is unclear whether the authors have difficulties publishing the preregistered study or whether they were referring to an ongoing project. `r sum(group_details_prereg$group_sorting_4)` researchers have worked on a Registered report that has not been published and
`r sum(group_details_prereg$group_sorting_5)` researchers have worked on a Registered report that had been published.

# Saving Data from 'Other' Group

```{r others}
# Filtering data
other_data <- raw_data %>% 
  filter(finished == "True",
         progress == "100",
         informed_consent == "Yes",
         group == "other" & other_attention == "4\nFour")

other_data <- other_data %>% 
  select(response_id, duration_in_seconds,group_sorting_1:group_sorting_5, other_hypothesis:other_qrp, planning:changed_comment, -control_attention, -prereg_attention, -other_attention)

other_data <- 
  other_data %>% 
  # Gather all the columns with "other_" prefix
  pivot_longer(
    cols = contains("other_"),
    names_to = "variable_names",
    values_to = "values"
  ) %>% 
  # Response was forced so all NA values mean that the participant was not member of that group
  # So we can drop them
  drop_na(values) %>% 
  # Delete prefix and convert character variables to numeric
  mutate(variable_names = str_remove(variable_names, "other_")) %>% 
  # Spread gathered columns to make the datatable tidy
  pivot_wider(
    names_from = variable_names,
    values_from = values
  )
colnames(other_data)[colnames(other_data) == 'desing'] <- 'design'

# Export Other Data
write_tsv(other_data, here::here("data/main/processed/PreregistrationEvaluation_Others_Processed.tsv"))
```

From the `r nrow(other_data)` respondents who were assigned neither to the preregistered group nor to the non-preregistered, `r sum(other_data$group_sorting_1 == 'Yes' & other_data$group_sorting_2 == 'No' & other_data$group_sorting_5 == 'No')` indicated that they made experience with preregistration but have not (yet) published a preregistration. Out of this subgroup, `r sum(other_data$group_sorting_4 == 'Yes' | other_data$group_sorting_5 == 'Yes')` researchers reported having made experience with Registered Reports, with `r sum(other_data$group_sorting_5 == 'Yes')` having published at least one. For consistency, we again exclude all respondents who have experience with Registered Reports, leaving a sample of `r sum(other_data$group_sorting_1 == 'Yes' & other_data$group_sorting_2 == 'No' & other_data$group_sorting_4 == 'No' & other_data$group_sorting_5 == 'No')` respondents. 
