---
title: "PreregistrationEvaluation_Pilot_Grouping"
author: "Marton Kovacs"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(writexl)
library(readxl)
```

# Import data

We extracted the responses of the researchers from their response email by hand and copied it in a google spreadsheet.

```{r, message = FALSE, warning = FALSE}
raw <- read_tsv(here::here("data/pilot/raw/PreregistrationEvaluation_Pilot_Raw_data.tsv"))
```

# Preparing the dataset for separation

For the separation we add a new variable for the separated answers called [response_01]. Each of the new separated answers for the same response will be copied to a new variable in the same row.

```{r}
separate <- 
  raw %>% 
  mutate(response_01 = NA_character_)
```

# Saving the dataset

```{r}
# write_xlsx(separate, here::here("data/pilot/processed/PreregistrationEvaluation_Pilot_Separating_data.xlsx"))
```

# Import data

We went through all the responses and separated the responses by their content from the same researcher into new variables.

```{r, message = FALSE, warning = FALSE}
separated <- read_tsv(here::here("data/pilot/processed/PreregistrationEvaluation_Pilot_Separated_data.tsv"))
```

# Dropped responses

We drop the responses that are not about preregistration (but explicitly talking about registered reports.)

We dropped one response because of this reason.

```{r}
separated <-
  separated %>% 
  filter(response_id != 35)
```

# Preparing the dataset for the coding

We are passing only half of the dataset for coding, and we will use the other half for the validation of the groups.

```{r}
code <-
  separated %>% 
  gather(key = "response_no", value = "response_separate", -response_id, -response_raw) %>% 
  drop_na() %>% 
  mutate(response_no = str_remove(response_no, "response_"),
         code = NA_character_) %>% 
  arrange(response_id) %>% 
  slice(1:69)
```

# Descriptive statistics of the responses

Number of respondents whose responses were used in further analysis:

```{r}
code %>% 
  distinct(response_id) %>% 
  count()
```

Distribution of the number of responses from each respondent:

```{r}
code %>% 
  group_by(response_no) %>% 
  count()
```

# Saving the dataset

```{r}
# write_xlsx(code, here::here("data/pilot/processed/PreregistrationEvaluation_Pilot_Coding_data.xlsx"))
```

# Import data

```{r, message = FALSE, warning = FALSE}
coded <- read_tsv(here::here("data/pilot/processed/PreregistrationEvaluation_Pilot_Coded_data.tsv"))
```

# Preparing the dataset for the grouping

```{r}
group <-
  coded %>% 
  filter(code != "insufficient information") %>% 
  group_by(code) %>% 
  count() %>% 
  mutate(group = NA_character_)
```

# Saving the dataset

```{r}
# write_xlsx(group, here::here("data/pilot/processed/PreregistrationEvaluation_Pilot_Grouping_data.xlsx"))
```

# Import data

```{r, message = FALSE, warning = FALSE}
grouped <- read_tsv(here::here("data/pilot/processed/PreregistrationEvaluation_Pilot_Grouped_data.tsv"))
```

# Preparing the groups for the creation of the dimensions

```{r}
items <-
  grouped %>% 
  filter(group != "insufficient information",
         group != "irrelevant content") %>% 
  distinct(group)
```

# Saving the dataset

```{r}
# write_xlsx(items, here::here("data/pilot/processed/PreregistrationEvaluation_Pilot_ItemCreation_data.xlsx"))
```

# Validation of the grouping process

```{r}
validation <-
  separated %>% 
  gather(key = "response_no", value = "response_separate", -response_id, -response_raw) %>% 
  drop_na() %>% 
  mutate(response_no = str_remove(response_no, "response_"),
         group_validation = NA_character_) %>% 
  arrange(response_id) %>% 
  slice(70:156)
```

# Create definition for the groups

```{r}
definition <-
  grouped %>% 
  filter(group != "insufficient information",
         group != "irrelevant content") %>% 
  group_by(group) %>% 
  summarise(definition = str_c(code, collapse = "; ")) %>% 
  mutate(definition = tolower(definition))
```

# Saving the dataset

```{r}
# Responses to be valdiated
# write_xlsx(validation, here::here("data/pilot/processed/PreregistrationEvaluation_Pilot_Validation_data.xlsx"))

# Definitions of the groups
# write_xlsx(definition, here::here("data/pilot/processed/PreregistrationEvaluation_Pilot_Definition_data.xlsx"))
```